case_studies

### 2023-11-20 scripts/workshop/case_studies.Rmd
move file
update case studies

Stealing this google scholar scraper from another project
```{r}
names <- tibble(species = gmpd_select$ParasiteCorrectedName)

@@

```

>>>>

Stealing this google scholar scraper from another project (doesn't always work)
```{r}
names <- tibble(species = gmpd_select$ParasiteCorrectedName)

@@

write_csv(names, here("data/scholar_results.csv"))
```
